Age-related changes in plant growth and traits

### 2016-05-19 scripts/Accessory_figs_20160218.Rmd
changing variable names making sure script runs adding in other lists to calculate "dispersal costs" - still in progress

plot(prop_prepollen_all~seed_size,SummarySpp[["mean"]],pch=16,log="x",col=col.spp(species))
mod <- sma(propagule_inv~seed_size,data=subset(SummarySpp[["mean"]],species!="EPMI"), log="xy",slope=1, method="OLS")
summary(mod)

@@

plot(prop_failure~seedset,data=subset(SummarySpp[["mean"]],species!="BAER"&species!="PEPU"),pch=16,log="",col=col.spp(species))
mod <- lm(prop_failure~seedset,data=subset(SummarySpp[["mean"]],species!="BAER"&species!="PEPU"))
summary(mod)

@@

mod <- lm(log10(seedcosts) ~prop_seedcosts,SummarySpp[["mean"]])
summary(mod)

mod <- lm(log10(seedcosts) ~prop_prepollencosts,SummarySpp[["mean"]])
summary(mod)

mod <- lm(log10(seedcosts) ~prop_dispersalcosts,SummarySpp[["mean"]])
summary(mod)

@@

#Table 1 showing accessory cost values for the species
```{r}
acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,seed_size,accessory_per_seed,prop_accessory_nonzero,seedcosts,prop_success,
                               prepollencosts,packaging_dispersal_per_seed,failure_per_seed,prop_failure,prepollen_failure_per_seed,postpollen_aborted_per_seed, seedset)
acc_costs_spp$species <- labels.spp.full()
acc_costs_spp <- format(acc_costs_spp, digit=2)

@@

#Figure 2. Ternary diagram showing seedcosts
```{r}
ternary <- select(SummarySpp[["mean"]],species,seed_size,prepollencosts,packaging_dispersal_per_seed)
ternary$packaging_dispersal_per_seed[9] <- 0.1

ternary$seedcosts = ternary$seed_size + ternary$prepollencosts + ternary$packaging_dispersal_per_seed
ternary$per_seed <-100*ternary$seed_size/ternary$seedcosts
ternary$per_poll <-100*ternary$prepollencosts/ternary$seedcosts
ternary$post_poll <- 100-ternary$per_poll

ternary$per_disp <-100*ternary$packaging_dispersal_per_seed/ternary$seedcosts
mod_poll <- sma(per_poll~seedcosts,ternary,slope.test=0,method="OLS",log="x")
mod_seed <- sma(per_seed~seedcosts,ternary,slope.test=0,method="OLS",log="x")
mod_disp <- sma(per_disp~seedcosts,ternary,slope.test=0,method="OLS",log="x")
mod_post_poll <- sma(post_poll~seedcosts,ternary,slope.test=0,method="OLS",log="x")

@@

plot(per_seed~seedcosts,ternary,col="black",log="x",pch=21,cex=2,ylim=c(0,75),ylab="prop of seedcosts")
points(per_poll~seedcosts,ternary,col="red",pch=16,cex=2)
points(per_disp~seedcosts,ternary,col="blue",pch=16,cex=2)

@@

plot(per_poll~seedcosts,ternary,col="black",log="x",pch=16,cex=2,ylim=c(0,100),ylab="prop of seedcosts")
points(post_poll~seedcosts,ternary,col="red",pch=16,cex=2)
abline(mod_poll$groupsummary["Int"][[1]],mod_poll$groupsummary["Slope"][[1]],col="black",lwd=2)
abline(mod_post_poll$groupsummary["Int"][[1]],mod_post_poll$groupsummary["Slope"][[1]],col="red",lwd=2)
summary(mod_post_poll)

@@

#Figure 2 continued
```{r}
win.metafile("figs2/Accessory_Costs/Figure03_ternary_diagram_seedcosts.wmf", height=5, width=5)
plot

@@

ggtern(data=ternary,aes(y=per_seed,x=per_poll,z=per_disp)) +
  labs(y = "seed",
       x = "pre-poll",
       z = "pack&disp",
       Tarrow = "seed weight (%)",
       Larrow = "pre-pollination costs (%)",
       Rarrow = "packaging & dispersal costs (%)",
       title = "Seed cost components",
       size = 3) +
  geom_point(size=sqrt(ternary$seedcosts/2),shape=20,color=col.spp()) +
   theme_bw() + 
  theme_showarrows() +
  geom_text(label=ternary$species, color="black", hjust=-.3, vjust=sqrt(ternary$seedcosts/500),size=2)

@@

#Table 2 showing seedcost breakdown into components, by species
```{r}
prop_seedcosts_spp <- dplyr::select(SummarySpp[["mean"]],species,seedcosts,prop_prepollencosts,prop_dispersalcosts,prop_seedcosts)
prop_seedcosts_spp$species <- labels.spp.full()
prop_seedcosts_spp <- format(prop_seedcosts_spp, digit=2)
write.csv(prop_seedcosts_spp, file="figs2/Accessory_Costs/Table04_Prop_seedcosts_by_Species.csv",row.names=FALSE)
```

#Figure 3. Scaling of accessory costs versus seed size, by species
```{r}
win.metafile("figs2/Accessory_Costs/Figure04_seed_size_acc_cost_correlations.wmf", height=5, width=15)
plot

@@

plot(prepollencosts~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required pre-pollination costs per seed (mg/seed)",xlab="",cex=1.5)
#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$prepollencosts,SummarySpp[["se"]]$prepollencosts)
mod <- lm(log10(prepollencosts)~log10(seed_size),SummarySpp[["mean"]])
abline(coef(mod)[1],coef(mod)[2])
abline(coef(mod)[1],1,col="red")
axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)

plot(packaging_dispersal_per_seed~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="packaging and dispersal costs per seed (mg/seed)",xlab="",cex=1.5)
#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$packaging_dispersal_per_seed,SummarySpp[["se"]]$prepollencosts)
mod <- lm(log10(packaging_dispersal_per_seed)~log10(seed_size),SummarySpp[["mean"]])
abline(coef(mod)[1],coef(mod)[2])
abline(coef(mod)[1],1,col="red")
axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
mtext(text="seed size (mg)",side=1,line=1.5,outer=TRUE)
dev.off()
```

@@

plot(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), xlim=c(.02,10000), ylab="total per seed accessory costs (mg/seed)",xlab="",cex=1.5)
mod <- lm(log10(accessory_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0))
y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
slopes <- sma(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
#abline(slopes$groupsummary["Int"][[1]],1,col="red")
abline(0,1,col="red")
words.bottom.right.logxy(mod)

@@

plot(prepollencosts ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen success costs (mg/seed)",xlab="",cex=1.5)
mod <- lm(log10(prepollencosts) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]))
words.bottom.right.logxy(mod)
extra.topleft.logxy("slope <1, so bigger seeded species have lower fixed costs of making pre-pollination parts")
slopes <- sma(prepollencosts ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,col="red")
acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

plot(prepollen_failure_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen failure costs (mg/seed)",xlab="",cex=1.5)
mod <- lm(log10(prepollen_failure_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]))
words.bottom.right.logxy(mod)
extra.topleft.logxy("the per seed costs of failure scale isometrically with seed size")
slopes <- sma(prepollen_failure_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,col="red")
y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$prepollen_failure_per_seed,SummarySpp[["se"]]$prepollen_failure_per_seed)
acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

@@

plot(postpollen_aborted_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]],species!="COER"),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted fruit accessory costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
mod <- lm(log10(postpollen_aborted_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0&species!="COER"&species!="BAER"))
words.top.left.logxy(mod)
y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$postpollen_aborted_per_seed,SummarySpp[["se"]]$postpollen_aborted_per_seed)
slopes <- sma(postpollen_aborted_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]],species!="COER"&species!="BAER"),slope.test=1, log="xy",method="OLS")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,col="red")
acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

plot(packaging_dispersal_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
mod <- lm(log10(packaging_dispersal_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],species!="LEES"))
words.top.left.logxy(mod)
slopes <- sma(packaging_dispersal_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]],species!="LEES"),slope.test=1, log="xy",method="OLS")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,col="red")
acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
mtext(text="seed size (mg)",side=1,line=1.5,outer=TRUE)

@@

acc_by_species$variable = c("total accessory costs","prepollen_success","prepollen_failure","total prepollen","c div p","dispersal","total postpollen")

write.csv(acc_by_species, file="figs2/Accessory_Costs/Table03_acc_cost_seed_size_slopes.csv",row.names=FALSE)
```
plot(prop_prepollen_all~seed_size,SummarySpp[["mean"]],pch=16,col=col.spp(species),log="x")

>>>>

#ideas in progress
``` {r}
plot(prop_prepollen_all~seed_size,SummarySpp[["mean"]],pch=16,log="x",col=col.spp(species))
mod <- sma(propagule_inv~seed_size,data=subset(SummarySpp[["mean"]],species!="EPMI"), log="xy",slope=1, method="OLS")
summary(mod)

@@

plot(prop_failure~seedset,data=subset(SummarySpp[["mean"]],species!="BAER"&species!="PEPU"),pch=16,log="",col=col.spp(species))
mod <- lm(prop_failure~seedset,data=subset(SummarySpp[["mean"]],species!="BAER"&species!="PEPU"))
summary(mod)
```

@@

mod <- lm(log10(seed_costs) ~prop_seed_costs,SummarySpp[["mean"]])
summary(mod)

mod <- lm(log10(seed_costs) ~prop_prepollen_costs,SummarySpp[["mean"]])
summary(mod)

mod <- lm(log10(seed_costs) ~prop_dispersalcosts,SummarySpp[["mean"]])
summary(mod)

@@

#Table 1 showing accessory cost values for the species
```{r}
acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,seed_size,accessory_per_seed,prop_accessory_nonzero,seed_costs,prop_success, prepollen_costs,packaging_dispersal_per_seed,failure_per_seed,prop_failure,prepollen_failure_per_seed,postpollen_aborted_per_seed, seedset)
acc_costs_spp$species <- labels.spp.full()
acc_costs_spp <- format(acc_costs_spp, digit=2)

@@

#Figure 2. Ternary diagram showing seed_costs
```{r}
ternary <- select(SummarySpp[["mean"]],species,seed_size,prepollen_costs,pack_disp_costs_corr)
ternary$pack_disp_costs_corr[9] <- 0.1

ternary$seed_costs = ternary$seed_size + ternary$prepollen_costs + ternary$pack_disp_costs_corr
ternary$per_poll <-100*ternary$prepollen_costs/ternary$seed_costs
ternary$post_poll <- 100-ternary$per_poll
ternary$per_seed <-100*ternary$seed_size/ternary$seed_costs
ternary$per_disp <-100*ternary$pack_disp_costs/ternary$seed_costs

mod_poll <- sma(per_poll~seed_costs,ternary,slope.test=0,method="OLS",log="x")
mod_seed <- sma(per_seed~seed_costs,ternary,slope.test=0,method="OLS",log="x")
mod_disp <- sma(per_disp~seed_costs,ternary,slope.test=0,method="OLS",log="x")
mod_post_poll <- sma(post_poll~seed_costs,ternary,slope.test=0,method="OLS",log="x")

@@

plot(per_seed~seed_costs,ternary,col="black",log="x",pch=21,cex=2,ylim=c(0,75),ylab="prop of seed_costs")
points(per_poll~seed_costs,ternary,col="red",pch=16,cex=2)
points(per_disp~seed_costs,ternary,col="blue",pch=16,cex=2)

@@

plot(per_poll~seed_costs,ternary,col="black",log="x",pch=16,cex=2,ylim=c(0,100),ylab="prop of seed_costs")
points(post_poll~seed_costs,ternary,col="red",pch=16,cex=2)
abline(mod_poll$groupsummary["Int"][[1]],mod_poll$groupsummary["Slope"][[1]],col="black",lwd=2)
abline(mod_post_poll$groupsummary["Int"][[1]],mod_post_poll$groupsummary["Slope"][[1]],col="red",lwd=2)
summary(mod_post_poll)

@@

#Figure 2 continued
```{r}
win.metafile("figs2/Accessory_Costs/Figure03_ternary_diagram_seed_costs.wmf", height=5, width=5)
plot

@@

ggtern(data=ternary,aes(y=per_seed,x=per_poll,z=per_disp)) +
  labs(y = "seed",
       x = "pre-poll",
       z = "pack&disp",
       Tarrow = "seed weight (%)",
       Larrow = "pre-pollination costs (%)",
       Rarrow = "packaging & dispersal costs (%)",
       title = "Seed cost components",
       size = 3) +
  geom_point(size=sqrt(ternary$seed_costs/2),shape=20,color=col.spp()) +
   theme_bw() + 
  theme_showarrows() +
  geom_text(label=ternary$species, color="black", hjust=-.3, vjust=sqrt(ternary$seed_costs/500),size=2)

@@

#Table 2 showing seedcost breakdown into components, by species
```{r}
prop_seed_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,seed_costs,prop_prepollen_costs,prop_dispersalcosts,prop_seed_costs)
prop_seed_costs_spp$species <- labels.spp.full()
prop_seed_costs_spp <- format(prop_seed_costs_spp, digit=2)
write.csv(prop_seed_costs_spp, file="figs2/Accessory_Costs/Table04_Prop_seed_costs_by_Species.csv",row.names=FALSE)
```
$embryo_endo_size

#Figure 3. Scaling of accessory costs versus seed size, by species
```{r}
win.metafile("figs2/Accessory_Costs/Figure03_seed_size_acc_cost_correlations.wmf", height=5, width=15)
plot

@@

plot(prepollen_costs~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required pollinator attraction costs per seed (mg/seed)",xlab="",cex=1.5)
#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["se"]]$prepollen_costs)
mod <- lm(log10(prepollen_costs)~log10(seed_size),SummarySpp[["mean"]])
abline(coef(mod)[1],coef(mod)[2])
abline(coef(mod)[1],1,col="red")
axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)

plot(postpollen_all_per_seed~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required provisioning costs per seed (mg/seed)",xlab="",cex=1.5)
#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$packaging_dispersal_per_seed,SummarySpp[["se"]]$prepollen_costs)
mod <- lm(log10(postpollen_all_per_seed)~log10(seed_size),SummarySpp[["mean"]])
abline(coef(mod)[1],coef(mod)[2])
abline(coef(mod)[1],1,col="red")
axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
mtext(text="seed size (mg)",side=1,line=1.5,outer=TRUE)
dev.off()
```

#Figure 3 v2. Scaling of accessory costs versus weight of embryo + endosperm, by species
```{r}
win.metafile("figs2/Accessory_Costs/Figure03_embryo_size_acc_cost_correlations.wmf", height=5, width=15)
plot

plot(accessory_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="total accessory costs per seed (mg/seed)",xlab="",cex=1.5)
mod <- lm(log10(accessory_per_seed) ~ log10(embryo_endo_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0))
words.top.left.logxy(mod)
y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
abline(coef(mod)[1],coef(mod)[2])
abline(coef(mod)[1],1,col="red")
axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)

plot(prepollen_costs~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required pollinator attraction costs per seed (mg/seed)",xlab="",cex=1.5)
y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["se"]]$prepollen_costs)
mod <- lm(log10(prepollen_costs)~log10(embryo_endo_size),SummarySpp[["mean"]])
words.top.left.logxy(mod)
abline(coef(mod)[1],coef(mod)[2])
abline(coef(mod)[1],1,col="red")
axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)

plot(postpollen_all_per_seed~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required provisioning costs per seed (mg/seed)",xlab="",cex=1.5)
y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$packaging_dispersal_per_seed,SummarySpp[["se"]]$prepollen_costs)
mod <- lm(log10(postpollen_all_per_seed)~log10(embryo_endo_size),SummarySpp[["mean"]])
words.top.left.logxy(mod)
abline(coef(mod)[1],coef(mod)[2])
abline(coef(mod)[1],1,col="red")
axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
mtext(text="embryo + endosperm (mg)",side=1,line=1.5,outer=TRUE)

@@

plot(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), xlim=c(.02,10000), ylab="total per seed accessory costs (mg/seed)",xlab="",cex=1.5)
mod <- lm(log10(accessory_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0))
y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
slopes <- sma(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,col="red")
words.bottom.left.logxy(mod)

@@

plot(prepollen_costs ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen success costs (mg/seed)",xlab="",cex=1.5)
y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["se"]]$prepollen_costs)
mod <- lm(log10(prepollen_costs) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]))
words.bottom.left.logxy(mod)
slopes <- sma(prepollen_costs ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,col="red")
acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

plot(failure_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen failure costs (mg/seed)",xlab="",cex=1.5)
mod <- lm(log10(failure_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]))
words.bottom.left.logxy(mod)
slopes <- sma(failure_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,col="red")
y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$failure_per_seed,SummarySpp[["se"]]$failure_per_seed)
acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

@@

# plot(postpollen_aborted_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]],species!="COER"),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted fruit accessory costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
# mod <- lm(log10(postpollen_aborted_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0&species!="COER"&species!="BAER"))
# words.top.left.logxy(mod)
# y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$postpollen_aborted_per_seed,SummarySpp[["se"]]$postpollen_aborted_per_seed)
# slopes <- sma(postpollen_aborted_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]],species!="COER"&species!="BAER"),slope.test=1, log="xy",method="OLS")
# abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
# abline(slopes$groupsummary["Int"][[1]],1,col="red")
# acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

plot(pack_disp_costs ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
mod <- lm(log10(pack_disp_costs) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]))
words.top.left.logxy(mod)
slopes <- sma(packaging_dispersal_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]],species!="LEES"),slope.test=1, log="xy",method="OLS")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,col="red")
y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$pack_disp_costs,SummarySpp[["se"]]$pack_disp_costs)
acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
mtext(text="seed size (mg)",side=1,line=1.5,outer=TRUE)

@@

acc_by_species$variable = c("total accessory costs","prepollen_success","failed_tissues","total prepollen","dispersal","total postpollen")

write.csv(acc_by_species, file="figs2/Accessory_Costs/Table03_acc_cost_seed_size_slopes.csv",row.names=FALSE)
```

#Table 3 v2. Slopes for various embryo size by acc cost regressions
```{r}
par(mfrow=c(2,3), cex=1, omi=c(.6,.1,.05,.05), mai=c(.1,.8,.05,.05)) 
options(scipen = 5)

plot(accessory_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), xlim=c(.02,10000), ylab="total per seed accessory costs (mg/seed)",xlab="",cex=1.5)
mod <- lm(log10(accessory_per_seed) ~ log10(embryo_endo_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0))
y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
slopes <- sma(accessory_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,col="red")
words.bottom.left.logxy(mod)

plot(prepollen_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen success costs (mg/seed)",xlab="",cex=1.5)
y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["se"]]$prepollen_costs)
mod <- lm(log10(prepollen_costs) ~ log10(embryo_endo_size),data=subset(SummarySpp[["mean"]]))
words.bottom.left.logxy(mod)
slopes <- sma(prepollen_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,col="red")
acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

plot(failure_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen failure costs (mg/seed)",xlab="",cex=1.5)
mod <- lm(log10(failure_per_seed) ~ log10(embryo_endo_size),data=subset(SummarySpp[["mean"]]))
words.bottom.left.logxy(mod)
slopes <- sma(failure_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,col="red")
y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$failure_per_seed,SummarySpp[["se"]]$failure_per_seed)
acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

plot(prepollen_all_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen failure costs (mg/seed)",xlab="",cex=1.5)
mod <- lm(log10(prepollen_all_per_seed) ~ log10(embryo_endo_size),data=subset(SummarySpp[["mean"]]))
words.bottom.right.logxy(mod)
slopes <- sma(prepollen_all_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,col="red")
y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$prepollen_all_per_seed,SummarySpp[["se"]]$prepollen_all_per_seed)
acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

# plot(postpollen_aborted_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]],species!="COER"),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted fruit accessory costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
# mod <- lm(log10(postpollen_aborted_per_seed) ~ log10(embryo_endo_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0&species!="COER"&species!="BAER"))
# words.top.left.logxy(mod)
# y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$postpollen_aborted_per_seed,SummarySpp[["se"]]$postpollen_aborted_per_seed)
# slopes <- sma(postpollen_aborted_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]],species!="COER"&species!="BAER"),slope.test=1, log="xy",method="OLS")
# abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
# abline(slopes$groupsummary["Int"][[1]],1,col="red")
# acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
